Introducing statistics with \texttt{intRo}

### 2015-11-23 jcgs-paper-2016/paper.Rmd
Discuss reproducibility more

@@

## Reproducibility

>>>>

## Reproducibility
Though they can make common actions quicker and interacting with software much simplier, many Graphical User Interfaces for scientific software packages come with a major drawback. That is, the actions taken by the user are typically not reproducible. Code scripting, on the other hand, allows us to share a file containing code, and another user can execute the code to reproduce the same results. In terms of the scientific process, where results can and should be scrutinized by other parties, the utility of GUIs are greatly limited.

We have designed \texttt{intRo} modules to reproduce actions taken by the user so that they can obtain \texttt{R} code associated with each module interacted with. When a user chooses to store the results associated with a particular module, R code yielding the visible results is automatically added to the code window at the bottom. This framework yields several advantages:

1. This eases a user who may be intimidated by programming into the idea that interacting with a user interface is really just a frontend for code. Seeing the correspondence between graphical clicks and printed code will hopefully also lessen the fear of coding that many inexperienced users may have.

2. An analysis created by \texttt{intRo} can be reproduced in an R session to easily assess and extend the results.

3. "Printing" the results of an \texttt{intRo} analysis amounts to nothing more than executing the R code on the server, adding another layer of reproducibility.

We designed the modules in such a way that the code printed to the console is the same as the code executed by the server, which makes the process of writing an \texttt{intRo} module significantly more seamless. The workhorse function for this reproducibility framework is called `interpolate`, which is based on a function proposed by Hadley Wickham[ref]. The idea of interpolation is that the call can be captured, printed, and evaluated, with all the appropriate arguments substituted into the call automatically. This means that depending on the options selected in \texttt{intRo}, the corresponding arguments to functions are appropriately set for reproduction in a standard R session.

```{r, eval=FALSE}
interpolate <- function(code, ..., mydir, `_env` = parent.frame(), file = "code_All.R", 
                        append = FALSE, save_result = FALSE, eval = TRUE) {
    stopifnot(inherits(code, "formula"), length(code) == 2)

    args <- lapply(list(...), as_call)
    expr <- methods::substituteDirect(as_call(code), args)

    cat(paste0(as.character(expr)[2], "\n"), file = file.path(mydir, file), append = append)

    if (save_result) cat(paste0(paste(readLines(file.path(mydir, file)), collapse = "\n"),
                                "\n"), file = file.path(mydir, "code_All.R"), append = TRUE)
    if (eval) eval(expr, `_env`)
}
```

@@
